Data Specialization for a Staged Lambda Calculus

### 2015-02-13 paper/figures/splitting-overview.tex

\hspace{2em} Evaluation Rule: $\sepredtwo {\pipeM c l r} {\mval i {[b/l]r}}$, where $b$ (also called the {\em boundary value}) is generated by $\reduce c {\tup{i,b}}$

>>>>

\hspace{2em} Evaluation Rule: $\sepredone {\pipeM c l r} {\mval i {[b/l]r}}$, where $b$ (also called the {\em boundary value}) is generated by $\reduce c {\tup{i,b}}$
